Localization properties, observable character and computational reliability of the linear response in open systems

### 2018-06-27 AnalyticStructure_main.tex
update

% Useful packages
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,braket}
\usepackage{tikz}%,pgfplots}
\usepackage{xifthen}
%\pgfplotsset{compat=1.15}

@@

@@

\begin{figure}[ht]
\centering
\subfloat[aaaa]
{\label{c6h6_excLand}
\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
\centering
\subfloat[bbbbb]
{\label{C6H6_exc}
\includegraphics[scale=0.6]{C6H6_dos.eps}}
\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
\end{figure}

@@

% We show that Casida equations are equivalent to the operator eigenvalue equations \eqref{ExcitationOperatorsDef1} when an explicit basis $\{\ket{\eta}\}$ for the empty states subspace is used,
% so that $\op Q_0 = \sum_{\eta}\ketbra{\eta}{\eta}$. Operators $\op O$ satisfying the transverse condition $\op O = \op O_{\perp}$ (see eq. \eqref{RhopTransverseDef1}) can be represented as 
% follows
% \be\lb{OperatorTransBasisExpDef1}
% \op O = \sum_{p\eta}\left(
% \excite{p}{\eta}\trace{\decay{\eta}{p}\op O} + \decay{\eta}{p}\trace{\excite{p}{\eta}\op O}
% \right) \;,
% \ee
% where the \emph{transition operators} $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$
% are normalized as follows
% \be
% \trace{\excite{p}{\eta}\excite{q}{\rho}} = \trace{\decay{\eta}{p}\decay{\rho}{q}} = 0 \;, \quad
% \trace{\excite{p}{\eta}\decay{\rho}{q}} = \delta_{pq}\delta_{\eta\rho} \;. \nonumber
% \ee
% Expanding equations \eqref{ExcitationOperatorsDef1} in the basis of transitions provides a matrix equation for the coefficients of the expansion. In particular from the left action equation
% one has
% \be
% \sum_{q\rho}\mat{\trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
% \trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \decay{\beta}{q}} \\
% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \decay{\beta}{q}}}
% \mat{X_a^{p\eta} \\ Y_a^{p\eta}} = \Omega_a \mat{X_a^{p\eta} \\ Y_a^{p\eta}}
% \ee

@@

>>>>

% Useful packages
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,braket}
\usepackage{tikz}
\usepackage{xifthen}
%\pgfplotsset{compat=1.15}

@@

\captionsetup{justification=centerlast}

@@

\begin{figure}[ht]
\centering
\subfloat[aaaa]
{\label{c6h6_excLand}
\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
\centering
\subfloat[bbbbb]
{\label{C6H6_exc}
\includegraphics[scale=0.58]{C6H6_dos.eps}}
\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
\end{figure}

@@

@@

\section{Computational details}

\subsection{$CO$}

Both GS and LR calculations for the $CO$ molecule are performed in three distinct computational setup that differs for the dimension of the computational
domain. The molecule is oriented along the $z$ axis and the $z$-dimension of the box is equal to 11.5, 15.1 and 16.6 \AA.

Excitation energies and states are obtained through the explicit diagonalization of the Casida matrix. To this scope we have built a basis in the domain of $\op Q_0$ 
by calculating the eigenvectors and associated energies of the empty virtual orbitals of $\hnot$. 280 states have been computed in each setup and the corresponding
energy cutoff in the three simulation box is 30.7, 19.3 and 15.4 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).

The DOS reported in figure \ref{CO_exc} are obtained by adding a complex shift of $8\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.

\subsection{$C_6H_6$}

Both GS and LR calculations for the $C_6H_6$ molecule are performed in three distinct computational setup that differs for the dimension of the computational
domain. The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.

Excitation energies and states are obtained through the explicit diagonalization of the Casida matrix. To this scope we have built a basis in the domain of $\op Q_0$ 
by calculating the eigenvectors and associated energies of the empty virtual orbitals of $\hnot$. 220 states have been computed in each setup and the corresponding
energy cutoff in the three simulation box is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).

The DOS reported in figure \ref{C6H6_exc} are obtained by adding a complex shift of $1.3\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
